legauo Amicus Brief Models

### 2022-05-16 modeling/amicus_type/forgauf.Rmd
add sgfem3 to base

* 0:
* 0.01:
* 0.05: 
* 0.10: health (-), standing (+)
* 0.20: bad law (+), morality & religion (+)

@@

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
                forgauf_abortion_regret,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                forgauf_bad_law,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                forgauf_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                forgauf_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
                forgauf_final_authority,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                forgauf_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
                forgauf_overturn_roe,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod18 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                forgauf_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
                forgauf_standing,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                forgauf_uncertainty,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                forgauf_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                forgauf_untruthful,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
                forgauf_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                forgauf_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                forgauf_womens_rights,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

>>>>

* 0:
* 0.01:
* 0.05: standing (+)
* 0.10: health (-) 
* 0.20: bad law (+), morality & religion (+)

@@

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                forgauf_abortion_regret,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                forgauf_bad_law,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                forgauf_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                forgauf_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                forgauf_final_authority,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                forgauf_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                forgauf_overturn_roe,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod18 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                forgauf_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                forgauf_standing,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                forgauf_uncertainty,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                forgauf_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                forgauf_untruthful,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                forgauf_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                forgauf_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                forgauf_womens_rights,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

### 2022-05-16 modeling/amicus_type/legauf.Rmd
add sgfem3 to base

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
                legauf_abortion_regret,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                legauf_bad_law,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                legauf_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                legauf_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
                legauf_final_authority,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                legauf_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
                legauf_overturn_roe,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod18 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                legauf_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
                legauf_standing,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                legauf_uncertainty,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                legauf_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                legauf_untruthful,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam +
                legauf_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                legauf_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + 
                legauf_womens_rights,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

>>>>

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                legauf_abortion_regret,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                legauf_bad_law,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                legauf_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                legauf_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                legauf_final_authority,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                legauf_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                legauf_overturn_roe,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod18 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                legauf_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                legauf_standing,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                legauf_uncertainty,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                legauf_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                legauf_untruthful,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 + 
                legauf_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                legauf_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + pfemam + sgfem3 +  
                legauf_womens_rights,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

### 2022-05-16 modeling/amicus_type/legauo.Rmd
add sgfem3 to base

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
                legauo_abortion_regret,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                legauo_bad_law,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                legauo_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                legauo_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
                legauo_final_authority,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                legauo_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
                legauo_overturn_roe,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod18 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                legauo_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
                legauo_standing,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                legauo_uncertainty,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                legauo_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                legauo_untruthful,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam +
                legauo_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                legauo_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + 
                legauo_womens_rights,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

>>>>

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                legauo_abortion_regret,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                legauo_bad_law,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                legauo_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                legauo_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                legauo_final_authority,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                legauo_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                legauo_overturn_roe,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod18 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                legauo_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                legauo_standing,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                legauo_uncertainty,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                legauo_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                legauo_untruthful,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 + 
                legauo_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                legauo_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + lcdisdirfem + poppam + sgfem3 +  
                legauo_womens_rights,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
